---
title: "Bivariate_maps_MaternalSyphilis_ENAHO"
author: "CardenasA"
date: "2024-08-05"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(ggplot2)
library(readr)
library(survey)
install.packages("ggspatial",repos = 'http://cran.us.r-project.org')
library(ggspatial)
install.packages(c("cowplot", "sf"),repos = 'http://cran.us.r-project.org')
library(cowplot)
library(sf)
install.packages("biscale", dependencies = TRUE,repos = 'http://cran.us.r-project.org')
library(biscale)
library(readxl)
library(patchwork)
```

Uploading Enaho data:
 
```{r, echo =FALSE}

data_enaho <- read_csv("Data_enaho/enaho2.csv")

data_ubigeo <- read_csv("Data_final/data_ubigeo_innovalab.csv")

departamentos <- read_sf("Límites - mapas/DEPARTAMENTOS_inei_geogpsperu_suyopomalia.shp")
#data_syphilis <- read_csv("Data_final/data_syphilis.csv")

data_enaho = rename(data_enaho, c("UBIGEO"="ubigeo"))

data_ubigeo = data_ubigeo %>%
  filter(year > 2014)

data_ubigeo = data_ubigeo [,c(8,10,12,14)]

data_ubigeo = distinct(data_ubigeo)

data_enaho <- data_enaho %>%
  left_join(data_ubigeo, by = c("UBIGEO")) %>%
  mutate(
    year = as.factor(data_enaho$year)
  ) %>%
  filter(
    sex == "woman"
  )
```

```{r include=FALSE}
rm(data_ubigeo)
```

Uploading MINSA data (maternal syphilis):

```{r, echo=FALSE}
maternal <- read_csv("Data_final/syphilis_maternal.csv")
newborn <- read_csv("Data_final/Nacidos_vivos_long.csv")
congenital <- read_csv("Data_final/syphilis_congenital.csv")

maternal = rename(
  maternal, c("NOMBDEP"="departamento","NOMBPROV"="provincia","NOMBDIST"="distrito"))

maternal_long <- pivot_longer(maternal, cols = c(4:11), 
                                names_to = "year", values_to = "maternal")

newborn = rename(
  newborn, c("NOMBDEP"="departamento","NOMBPROV"="provincia","year"="years")) %>%
group_by(NOMBDEP, year) %>%
filter( year > 2014) %>%
summarise(newborn =sum(n, na.rm = TRUE)) %>%
ungroup()

```

```{r}

data_maternal_dep <- maternal_long %>%
group_by(NOMBDEP, year) %>%
filter( year > 2014) %>%
summarise(maternal =sum(maternal, na.rm = TRUE)) %>%
mutate(year=as.numeric(year))%>%
ungroup()

#Calculating rates of maternal syphilis 
data_maternal_dep <- data_maternal_dep %>%
  left_join(newborn, by = c("NOMBDEP","year")) %>%
  mutate(rate_mat = (maternal/newborn)*1000) %>% 
  mutate_if(is.numeric, round, 2) %>%
  mutate(year = as.character(year))

```

```{r warning=FALSE}
## Maternal syphilis and poverty
poverty = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  select(poverty,year,NOMBDEP,conglome,estrato,facpob07,rate_mat) %>%
  filter(!is.na(poverty))%>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    poverty = as.factor(poverty)
  ) 


# Crear el diseño de muestreo estratificado
design <- svydesign(~ conglome, strata = ~ estrato, weights = ~ facpob07, data = poverty, nest = TRUE)

options(survey.lonely.psu="adjust")

syphilis_poverty<- svyby(~poverty,~NOMBDEP+year,svymean,design=design,deff=TRUE,na.rm=TRUE)

syphilis_poverty = as.data.frame(syphilis_poverty) 
syphilis_poverty <- syphilis_poverty %>%
  mutate(year = as.character(year))  %>%
  left_join(data_maternal_dep, by = c("NOMBDEP", "year")) %>%
  left_join(departamentos, by = "NOMBDEP")

custom_pal2 <- c(
  "1-1" = "#D2EEEA", # low x, low y
  "2-1" = "#3B99B1", # high x, low y
  "1-2" = "#6FB798", # low x, high y
  "2-2" = "#2A5676" # high x, high y
)
```

# Bivariate graphic of the rate of congenital syphilis and extreme poverty
in the departments of Peru

```{r echo=FALSE, fig.height=6, fig.width=8, warning=FALSE}

datamap <- bi_class(syphilis_poverty, x = rate_mat, y = povertypoor, style = "quantile", dim = 2)

map_poverty <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  # labs(
  #   title = "Total"
  # ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend_poverty <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "Poverty",
                    size = 10)

# combine map with legend
finalPlot_poverty_ms <- ggdraw() +
  draw_plot(map_poverty, 0, 0, 1, 1) +
  draw_plot(legend_poverty, .75, .6, .2, .2)

finalPlot_poverty_ms
```

```{r, echo=FALSE, fig.height=6, fig.width=8}
#2015

syphilis_poverty15 = syphilis_poverty %>%
  filter(
    year == "2015"
  )
datamap <- bi_class(syphilis_poverty15, x = rate_mat, y = povertypoor, style = "quantile", dim = 2)

map15 <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  labs(
    title = "2015"
      #"Rate of congenital syphilis in extremely poor pregnants in 2015"
  ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "Poverty",
                    size = 10)

# combine map with legend
finalPlot15 <- ggdraw() +
  draw_plot(map15, 0, 0, 1, 1) +
  draw_plot(legend, .75, .6, .2, .2)

finalPlot15
```

```{r, echo=FALSE, fig.height=6, fig.width=8}
#2018

syphilis_poverty18 = syphilis_poverty %>%
  filter(
    year == "2018"
  )

datamap <- bi_class(syphilis_poverty18, x = rate_mat, y = povertypoor, style = "quantile", dim = 2)

map18 <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  labs(
    title = "2018"
      #"Rate of congenital syphilis in extremely poor pregnants in 2018"
  ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "Poverty",
                    size = 10)

# combine map with legend
finalPlot18 <- ggdraw() +
  draw_plot(map18, 0, 0, 1, 1) +
  draw_plot(legend, .75, .6, .2, .2)

finalPlot18
```

```{r, echo=FALSE, fig.height=6, fig.width=8}
#2022

syphilis_poverty22 = syphilis_poverty %>%
  filter(
    year == "2022"
  )

datamap <- bi_class(syphilis_poverty22, x = rate_mat, y = povertypoor, style = "quantile", dim = 2)

map22 <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  labs(
    title = "2022"
    #  "Rate of congenital syphilis in extremely poor pregnants in 2018"
  ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "Poverty",
                    size = 10)


# combine map with legend
finalPlot22 <- ggdraw() +
  draw_plot(map22, 0, 0, 1, 1) +
  draw_plot(legend, .75, .6, .2, .2)

finalPlot22
```


```{r, echo = FALSE,fig.height = 5, fig.width = 10}
legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "Poverty",
                    size = 10)

mappoverty <- map_poverty | map15 | map18 |map22 | (legend/plot_spacer())
 #+ plot_layout(widths = c(1, 1, 1, 1, 1))

mappoverty
```

EDUCATION:

```{r warning=FALSE}
## Congenital syphilis and education
education = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(education_level,year,NOMBDEP,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(education_level))%>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    education_level = as.factor(education_level)
  ) 


# Crear el diseño de muestreo estratificado
design <- svydesign(~ conglome, strata = ~ estrato, weights = ~ facpob07, data = education, nest = TRUE)

options(survey.lonely.psu="adjust")

syphilis_education<- svyby(~education_level,~NOMBDEP+year,svymean,design=design,deff=TRUE,na.rm=TRUE)

syphilis_education = as.data.frame(syphilis_education) 
syphilis_education <- syphilis_education %>%
  mutate(year = as.character(year))  %>%
  left_join(data_congenital_dep, by = c("NOMBDEP", "year")) %>%
  left_join(data_maternal_dep, by = c("NOMBDEP", "year")) %>%
  left_join(departamentos, by = "NOMBDEP") %>%
  rename("less_than_secondary" = `education_levelless than secondary`)

```

# Bivariate graphic of the rate of congenital syphilis and level education
in the departments of Peru

```{r echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

datamap <- bi_class(syphilis_education, x = rate_mat, y = less_than_secondary, style = "quantile", dim = 2)

map_education <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  # labs(
  #   title = "Total"
  # ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend_education <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "Lower education",
                    size = 10)

# combine map with legend
finalPlot_education_ms <- ggdraw() +
  draw_plot(map_education, 0, 0, 1, 1) +
  draw_plot(legend_education, .75, .6, .2, .2)

finalPlot_education_ms
```

```{r, echo=FALSE, fig.height=8, fig.width=10}
#2015

syphilis_education15 = syphilis_education %>%
  filter(
    year == "2015"
  )

datamap <- bi_class(syphilis_education15, x = rate_mat, y = less_than_secondary, style = "quantile", dim = 2)


map15 <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  labs(
    title = "2015"
  ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  


legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Higher rate",
                    ylab = "Lower education",
                    size = 10)

# combine map with legend
finalPlot15 <- ggdraw() +
  draw_plot(map15, 0, 0, 1, 1) +
  draw_plot(legend, .75, .6, .2, .2)

finalPlot15
```

```{r, echo=FALSE, fig.height=8, fig.width=10}
#2018

syphilis_education18 = syphilis_education %>%
  filter(
    year == "2018"
  )

datamap <- bi_class(syphilis_education18, x = rate_mat, y = less_than_secondary, style = "quantile", dim = 2)

map18 <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  labs(
    title = "2018"
  ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Higher rate",
                    ylab = "Lower education",
                    size = 10)

# combine map with legend
finalPlot18 <- ggdraw() +
  draw_plot(map18, 0, 0, 1, 1) +
  draw_plot(legend, .75, .6, .2, .2)

finalPlot18
```

```{r, echo=FALSE, fig.height=8, fig.width=10}
#2022

syphilis_education22 = syphilis_education %>%
  filter(
    year == "2022"
  )

datamap <- bi_class(syphilis_education22, x = rate_mat, y = less_than_secondary, style = "quantile", dim = 2)

map22 <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  labs(
    title = "2022"
  ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Higher rate",
                    ylab = "Lower education",
                    size = 10)

# combine map with legend
finalPlot22 <- ggdraw() +
  draw_plot(map22, 0, 0, 1, 1) +
  draw_plot(legend, .75, .6, .2, .2)

finalPlot22
```

```{r, echo = FALSE,fig.height = 5, fig.width = 10}
legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "Primary education",
                    size = 10)

mapeducation <- map_education | map15 | map18 |map22 | (legend/plot_spacer())
 #+ plot_layout(widths = c(1, 1, 1, 1, 1))

mapeducation
```

Prenatal Care


```{r warning=FALSE}
## Congenital syphilis and prenatal visits
precare = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  select(prenatal_visit, year,NOMBDEP,conglome,estrato,facpob07,rate_mat) %>%
  filter(!is.na(prenatal_visit))%>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    prenatal_visit = as.factor(prenatal_visit)
  ) 


# Crear el diseño de muestreo estratificado
design <- svydesign(~ conglome, strata = ~ estrato, weights = ~ facpob07, data = precare, nest = TRUE)

options(survey.lonely.psu="adjust")

syphilis_precare<- svyby(~prenatal_visit,~NOMBDEP+year,svymean,design=design,deff=TRUE,na.rm=TRUE)

syphilis_precare = as.data.frame(syphilis_precare) 
syphilis_precare <- syphilis_precare %>%
  mutate(year = as.character(year))  %>%
  left_join(data_maternal_dep, by = c("NOMBDEP", "year")) %>%
  left_join(departamentos, by = "NOMBDEP")

```

# Bivariate graphic of the rate of congenital syphilis and prenatal care
in the departments of Peru

```{r echo=FALSE, fig.height=6, fig.width=8, warning=FALSE}

datamap <- bi_class(syphilis_precare, x = rate_mat, y = prenatal_visitno, style = "quantile", dim = 2)

map_precare <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  # labs(
  #   title = "Total"
  # ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend_precare <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "No prenatal visit",
                    size = 10)

# combine map with legend
finalPlot_precare <- ggdraw() +
  draw_plot(map_precare, 0, 0, 1, 1) +
  draw_plot(legend_precare, .75, .6, .2, .2)

finalPlot_precare
```

```{r, echo=FALSE, fig.height=6, fig.width=8}
#2015

syphilis_precare15 = syphilis_precare %>%
  filter(
    year == "2015"
  )
datamap <- bi_class(syphilis_precare15, x = rate_mat, y = prenatal_visitno, style = "quantile", dim = 2)

map15 <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  labs(
    title = "2015"
  ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "No prenatal visit",
                    size = 10)

# combine map with legend
finalPlot15 <- ggdraw() +
  draw_plot(map15, 0, 0, 1, 1) +
  draw_plot(legend, .75, .6, .2, .2)

finalPlot15
```

```{r, echo=FALSE, fig.height=6, fig.width=8}
#2018

syphilis_precare18 = syphilis_precare %>%
  filter(
    year == "2018"
  )
datamap <- bi_class(syphilis_precare18, x = rate_mat, y = prenatal_visitno, style = "quantile", dim = 2)

map18 <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  labs(
    title = "2018"
  ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "No prenatal visit",
                    size = 10)

# combine map with legend
finalPlot18 <- ggdraw() +
  draw_plot(map18, 0, 0, 1, 1) +
  draw_plot(legend, .75, .6, .2, .2)

finalPlot18
```

```{r, echo=FALSE, fig.height=6, fig.width=8}
#2022

syphilis_precare22 = syphilis_precare %>%
  filter(
    year == "2022"
  )
datamap <- bi_class(syphilis_precare22, x = rate_mat, y = prenatal_visitno, style = "quantile", dim = 2)

map15 <- ggplot() +
  geom_sf(data = datamap, mapping = aes(geometry= geometry, fill = bi_class), 
          color = "black", size = 0.1, show.legend = FALSE) +
  bi_scale_fill(pal = custom_pal2, dim = 2) +
  labs(
    title = "2022"
      #"Rate of congenital syphilis in extremely poor pregnants in 2015"
  ) +
  bi_theme() +
  theme(plot.title = element_text(size = rel(1))) 
  

legend <- bi_legend(pal = custom_pal2,
                    dim = 2,
                    xlab = "Rate",
                    ylab = "No prenatal visit",
                    size = 10)


# combine map with legend
finalPlot22 <- ggdraw() +
  draw_plot(map22, 0, 0, 1, 1) +
  draw_plot(legend, .75, .6, .2, .2)

finalPlot22
```

```{r, echo = FALSE,fig.height = 5, fig.width = 10}

mapprecare <- map_precare | map15 | map18 |map22 | (legend/plot_spacer())
 #+ plot_layout(widths = c(1, 1, 1, 1, 1))

mapprecare
```

```{r, echo = FALSE,fig.height = 4, fig.width = 10}

maptotals_maternal <- (map_poverty | legend_poverty | map_education | legend_education | map_precare | legend_precare) + plot_layout(widths = c(1, 0.6, 1, 0.6, 1, 0.6)) + 
  plot_annotation(
  title = 'Maternal Syphilis') 


maptotals_maternal
```

```{r}
#ggsave("Figures/Bivariate_maternal.png", plot = maptotals_maternal, width = 10, height = 4, dpi = 300)
```

```{r, echo = FALSE,fig.height = 8, fig.width = 10}

maptotals_final <- (maptotals / maptotals_maternal)

maptotals_final
```

