---
title: "Determinantes_reg_natural"
output: html_document
date: "2024-07-19"
---

```{r}
library(sf)
library(purrr)
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(readr)
library(survey)
library(gridExtra)
library(cowplot)
library(readxl)
library(wesanderson)
library(patchwork)
library(RSQLite)
```

```{r}
knitr::opts_chunk$set(
	echo = FALSE,
	cache = FALSE,
	dev = "png",
	dpi = 300
)
```

```{r}
data_enaho <- read_csv("Data_enaho/enaho2.csv")

data_ubigeo <- read_csv("Data_final/data_ubigeo_innovalab.csv")

departamentos <- read_sf("Límites - mapas/DEPARTAMENTOS_inei_geogpsperu_suyopomalia.shp")
#data_syphilis <- read_csv("Data_final/data_syphilis.csv")

data_enaho = rename(data_enaho, c("UBIGEO"="ubigeo"))

data_ubigeo = data_ubigeo %>%
  filter(year > 2014)

data_ubigeo = data_ubigeo [,c(8,10,12,14)]

data_ubigeo = distinct(data_ubigeo)

data_enaho <- data_enaho %>%
  left_join(data_ubigeo, by = c("UBIGEO")) %>%
  mutate(
    year = as.numeric(data_enaho$year),
    region_natural = case_when(NOMBDEP == "TUMBES"|NOMBDEP == "PIURA"|NOMBDEP == "LAMBAYEQUE"|NOMBDEP == "LA LIBERTAD"|NOMBDEP == "ANCASH"|NOMBDEP == "LIMA"|NOMBDEP == "CALLAO"|NOMBDEP == "ICA"|NOMBDEP == "AREQUIPA"|NOMBDEP == "MOQUEGUA"|NOMBDEP == "TACNA" ~ "COSTA",
                               NOMBDEP == "CAJAMARCA"|NOMBDEP == "HUANUCO"|NOMBDEP == "PASCO"|NOMBDEP == "JUNIN"|NOMBDEP == "HUANCAVELICA"|NOMBDEP == "AYACUCHO"|NOMBDEP == "APURIMAC"|NOMBDEP == "CUSCO"|NOMBDEP == "PUNO" ~ "SIERRA",
                               NOMBDEP == "AMAZONAS"|NOMBDEP == "SAN MARTIN"|NOMBDEP == "LORETO"|NOMBDEP == "UCAYALI"|NOMBDEP == "MADRE DE DIOS" ~ "SELVA")
  )

rm(data_syphilis,data_ubigeo)
```

Uploading MINSA data (maternal and congenital syphilis):
```{r, echo=FALSE}
maternal <- read_csv("Data_final/syphilis_maternal.csv")
newborn <- read_csv("Data_final/Nacidos_vivos_long.csv")
newborn_distrito <- read_excel("Data_final/Reniec_Nacimientos_Distritos.xlsx")

newborn_distrito = newborn_distrito %>% 
  mutate(across(c(NOMBDEP, NOMBPROV, NOMBDIST),
                ~ toupper(.x) %>%
                  stringi::stri_trans_general("Latin-ASCII")))

maternal = rename(
  maternal, c("NOMBDEP"="departamento","NOMBPROV"="provincia","NOMBDIST"="distrito"))
newborn = rename(
  newborn, c("NOMBDEP"="departamento","NOMBPROV"="provincia","year"="years"))

maternal_long <- pivot_longer(maternal, cols = c(4:11), 
                                names_to = "year", values_to = "maternal")

congenital <- read_csv("Data_final/syphilis_congenital.csv")

congenital <- congenital %>%
  select(!c(1))

congenital <- rename(
  congenital, c("NOMBDEP"="DEPARTAMENTO","NOMBPROV"="PROVINCIA","NOMBDIST"="DISTRITO"))

congenital_long <- pivot_longer(congenital, cols = c(4:12), 
                                names_to = "year", values_to = "congenital")

#Provincial
newborn_prov <- newborn %>%
  group_by(NOMBDEP, NOMBPROV, year) %>%
  summarise(newborntotal =sum(n, na.rm = TRUE)) %>%
  ungroup()

rm(maternal,congenital,newborn)
```

Maternal
```{r}
data_maternal_prov <- maternal_long %>%
  group_by(NOMBDEP, NOMBPROV, year) %>%
  filter( year > 2014) %>%
  summarise(maternal =sum(maternal, na.rm = TRUE)) %>%
  mutate(year=as.numeric(year))%>%
  ungroup()

#Calculating rates of maternal syphilis 
data_maternal_prov <- data_maternal_prov %>%
  left_join(newborn_prov, by = c("NOMBDEP","NOMBPROV","year")) %>%
  mutate(rate_mat = (maternal/newborntotal)*1000)
```

Congenital:
```{r}
congenital_long$year = as.numeric(congenital_long$year) 

#Provincial
congenital_long_prov <- congenital_long %>%
  group_by(NOMBDEP,NOMBPROV, year) %>%
  summarise(congenital = sum(congenital, na.rm = TRUE)) %>%
  unnest(congenital)

data_congenital_prov <- congenital_long_prov %>%
  left_join(newborn_prov, by = c("NOMBDEP","NOMBPROV","year")) %>%
  mutate(rate_con = (congenital/newborntotal)*1000) %>% 
  mutate_if(is.numeric, round, 2) %>%
  filter(rate_con < 100.0)

rm(congenital_long,congenital_long_dep,congenital_long_nac,newborn_nac,newborn_dep,data_ins_long,newborn_nac,newborn_dep)
```

# Poverty National
```{r}
poverty = 
  data_enaho %>%
  left_join(data_maternal_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  left_join(data_congenital_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  select(poverty,year, region_natural, NOMBDEP,NOMBPROV,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(poverty))%>%
  filter(year > "2014") %>%
  mutate(
    NOMBPROV = as.factor(NOMBPROV),
    year = as.factor(year),
    poverty = as.factor(poverty)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## TERCILES

Poverty objective 2 (terciles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_mr$povertypoor, probs = c(1/3, 2/3))*100

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <16.48 ~ "First tercile",
                            poverty >=16.48 & poverty <29.38 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

summary(poverty_mr$rate_mat_mean)

poverty_mr %>% 
     DT::datatable()
```

```{r}
selected_colors <- wes_palette("Zissou1", n = 5)[c(1, 3, 5)]
```

```{r}
National_obj2 =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod, color = poverty_cod))+
  geom_line(size = 1.2)+
  xlab("Years") +
  ylab("Rate") +
  ylim(0,18) +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

National_obj2 <- National_obj2 +
  ggtitle("Maternal - National") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

Poverty objective 3 (terciles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_cr$povertypoor, probs = c(1/3, 2/3))*100

poverty_cr = poverty_cr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <14.00 ~ "First tercile",
                            poverty >=14.00 & poverty <25.56 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
  summarize(
    objective = 0.5,
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

summary(poverty_cr$rate_con_mean)

poverty_cr %>% 
     DT::datatable()
```

```{r}
National_obj3 =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_line(aes(y=objective),color = "black", linetype = "dashed", size=1.2) +
  xlab("Years") +
  ylab("Rate") +
  ylim(0,8) +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

National_obj3  <- National_obj3  +
  ggtitle("Congenital - National") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

# Poverty Costa
```{r}
poverty = 
  data_enaho %>%
  left_join(data_maternal_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  left_join(data_congenital_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  select(poverty,year, region_natural, NOMBDEP,NOMBPROV,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(poverty))%>%
  filter(year > "2014") %>%
  filter(region_natural== "COSTA") %>%
  mutate(
    NOMBPROV = as.factor(NOMBPROV),
    year = as.factor(year),
    poverty = as.factor(poverty)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## TERCILES

Poverty Costa objective 2 (terciles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_mr$povertypoor, probs = c(1/3, 2/3))*100

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <10.12 ~ "First tercile",
                            poverty >=10.12 & poverty <21.30 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

summary(poverty_mr$rate_mat_mean)

poverty_mr %>% 
     DT::datatable()
```

```{r}
Costa_obj2 =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  xlab("Years") +
  ylab("Rate") +
  ylim(0,18) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Costa_obj2 <- Costa_obj2 +
  ggtitle("Maternal - Coast") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

Poverty Costa objective 3 (terciles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_cr$povertypoor, probs = c(1/3, 2/3))*100

poverty_cr = poverty_cr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <9.85 ~ "First tercile",
                            poverty >=9.85 & poverty <18.13 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
  summarize(
    objective = 0.5,
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

summary(poverty_cr$rate_con_mean)

poverty_cr %>% 
     DT::datatable()
```

```{r}
Costa_obj3 =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_line(aes(y=objective),color = "black", linetype = "dashed", size=1.2) +
  xlab("Years") +
  ylab("Rate") +
  ylim(0,8) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Costa_obj3  <- Costa_obj3  +
  ggtitle("Congenital - Coast") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

# Poverty Sierra
```{r}
poverty = 
  data_enaho %>%
  left_join(data_maternal_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  left_join(data_congenital_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  select(poverty,year, region_natural, NOMBDEP,NOMBPROV,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(poverty))%>%
  filter(year > "2014") %>%
  filter(region_natural== "SIERRA") %>%
  mutate(
    NOMBPROV = as.factor(NOMBPROV),
    year = as.factor(year),
    poverty = as.factor(poverty)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## TERCILES

Poverty Sierra objective 2 (terciles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_mr$povertypoor, probs = c(1/3, 2/3))*100

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <23.27 ~ "First tercile",
                            poverty >=23.27 & poverty <35.67 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

summary(poverty_mr$rate_mat_mean)

poverty_mr %>% 
     DT::datatable()
```

```{r}
Sierra_obj2 =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  xlab("Years") +
  ylab("Rate") +
  ylim(0,18) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Sierra_obj2 <- Sierra_obj2 +
  ggtitle("Maternal - Highlands") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))+
  scale_color_manual(values = selected_colors)
```

Poverty Sierra objective 3 (terciles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_cr$povertypoor, probs = c(1/3, 2/3))*100

poverty_cr = poverty_cr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <20.49 ~ "First tercile",
                            poverty >=20.49 & poverty <33.89 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
  summarize(
    objective=0.5,
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

summary(poverty_cr$rate_con_mean)

poverty_cr %>% 
     DT::datatable()
```

```{r}
Sierra_obj3 =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_line(aes(y=objective),color = "black", linetype = "dashed", size=1.2) +
  xlab("Years") +
  ylab("Rate") +
  ylim(0,8) +
  theme_bw() +
  theme(
   axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Sierra_obj3  <- Sierra_obj3  +
  ggtitle("Congenital - Highlands") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

# Poverty Selva
```{r}
poverty = 
  data_enaho %>%
  left_join(data_maternal_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  left_join(data_congenital_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  select(poverty,year, region_natural, NOMBDEP,NOMBPROV,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(poverty))%>%
  filter(year > "2014") %>%
  filter(region_natural== "SELVA") %>%
  mutate(
    NOMBPROV = as.factor(NOMBPROV),
    year = as.factor(year),
    poverty = as.factor(poverty)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## TERCILES

Poverty Selva objective 2 (terciles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_mr$povertypoor, probs = c(1/3, 2/3))*100

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <16.82 ~ "First tercile",
                            poverty >=16.82 & poverty <27.78 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

summary(poverty_mr$rate_mat_mean)

poverty_mr %>% 
     DT::datatable()
```

```{r}
Selva_obj2 =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  xlab("Years") +
  ylab("Rate") +
  ylim(0,18) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Selva_obj2 <- Selva_obj2 +
  ggtitle("Maternal - Jungle") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))+
  scale_color_manual(values = selected_colors)
```

Poverty Selva objective 3 (terciles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_cr$povertypoor, probs = c(1/3, 2/3))*100

poverty_cr = poverty_cr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <16.86 ~ "First tercile",
                            poverty >=16.86 & poverty <26.36 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
  summarize(
    objective = 0.5,
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

summary(poverty_cr$rate_con_mean)

poverty_cr %>% 
     DT::datatable()
```

```{r}
Selva_obj3 =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_line(aes(y=objective),color = "black", linetype = "dashed", size=1.2) +
  xlab("Years") +
  ylab("Rate") +
  ylim(0,8) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Selva_obj3  <- Selva_obj3  +
  ggtitle("Congenital - Jungle") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

## Gráfico general
```{r, fig.height=6, fig.width=12}
combined_plot <- National_obj3 + Costa_obj3 + Sierra_obj3 + Selva_obj3 + National_obj2 + Costa_obj2 + Sierra_obj2 +  Selva_obj2 + 
  plot_layout(ncol = 4, guides = 'collect') &  
  theme(legend.position = 'bottom')

Poverty_graph  <- combined_plot + 
  plot_annotation(
    title = "Poverty", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
    )
  )

Poverty_graph
ggsave("Poverty.png", plot = Poverty_graph)
```

# Education National
```{r}
education = 
  data_enaho %>%
  left_join(data_maternal_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  left_join(data_congenital_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  select(education_level,year, region_natural, NOMBDEP,NOMBPROV,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(education_level))%>%
  filter(year > "2014") %>%
  mutate(
    NOMBPROV = as.factor(NOMBPROV),
    year = as.factor(year),
    education = as.factor(education_level)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## TERCILES

Poverty objective 2 (terciles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_mr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <61.03 ~ "First tercile",
                             education >=61.03 & education <76.80 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

summary(education_mr$rate_mat_mean)

education_mr %>% 
     DT::datatable()
```

```{r}
National_obj2 =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  xlab("Years") +
  ylab("Rate") +
  ylim(0,14) +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

National_obj2 <- National_obj2 +
  ggtitle("Maternal - National") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))+
  scale_color_manual(values = selected_colors)
```

Poverty objective 3 (terciles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_cr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_cr = education_cr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <58.79 ~ "First tercile",
                             education >=58.79 & education <74.09 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
      objective = 0.5,
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

summary(education_cr$rate_con_mean)

education_cr %>% 
     DT::datatable()
```

```{r}
National_obj3 =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_line(aes(y=objective),color = "black", linetype = "dashed", size=1.2) +
  xlab("Years") +
  ylab("Rate") +
  ylim(0,6) +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

National_obj3  <- National_obj3  +
  ggtitle("Congenital - National") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

# Education Costa
```{r}
education = 
  data_enaho %>%
  left_join(data_maternal_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  left_join(data_congenital_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  select(education_level,year, region_natural, NOMBDEP,NOMBPROV,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(education_level))%>%
  filter(year > "2014") %>%
  filter(region_natural== "COSTA") %>%
  mutate(
    NOMBPROV = as.factor(NOMBPROV),
    year = as.factor(year),
    education = as.factor(education_level)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## TERCILES

Costa Poverty objective 2 (terciles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_mr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <49.43 ~ "First tercile",
                             education >=49.43& education <66.00 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

summary(education_mr$rate_mat_mean)

education_mr %>% 
     DT::datatable()
```

```{r}
Costa_obj2 =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  xlab("Years") +
  ylab("Rate") +
  ylim(0,14) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Costa_obj2  <- Costa_obj2  +
  ggtitle("Maternal - Coast") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

Costa Poverty objective 3 (terciles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_cr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_cr = education_cr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <46.55 ~ "First tercile",
                             education >=46.55 & education <61.60 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
      objective = 0.5,
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

summary(education_cr$rate_con_mean)

education_cr %>% 
     DT::datatable()
```

```{r}
Costa_obj3 =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_line(aes(y=objective),color = "black", linetype = "dashed", size=1.2) +
  xlab("Years") +
  ylab("Rate") +
  ylim(0,6) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Costa_obj3  <- Costa_obj3  +
  ggtitle("Congenital - Coast") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

# Education Sierra
```{r}
education = 
  data_enaho %>%
  left_join(data_maternal_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  left_join(data_congenital_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  select(education_level,year, region_natural, NOMBDEP,NOMBPROV,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(education_level))%>%
  filter(year > "2014") %>%
  filter(region_natural== "SIERRA") %>%
  mutate(
    NOMBPROV = as.factor(NOMBPROV),
    year = as.factor(year),
    education = as.factor(education_level)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## TERCILES

Sierra Poverty objective 2 (terciles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_mr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <68.40 ~ "First tercile",
                             education >=68.40 & education <81.58 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

summary(education_mr$rate_mat_mean)

education_mr %>% 
     DT::datatable()
```

```{r}
Sierra_obj2 =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  xlab("Years") +
  ylab("Rate") +
  ylim(0,14) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Sierra_obj2  <- Sierra_obj2  +
  ggtitle("Maternal - Highlands") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

Sierra Poverty objective 3 (terciles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_cr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_cr = education_cr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <65.33 ~ "First tercile",
                             education >=65.33 & education <78.81 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
      objective = 0.5,
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

summary(education_cr$rate_con_mean)

education_cr %>% 
     DT::datatable()
```

```{r}
Sierra_obj3 =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_line(aes(y=objective),color = "black", linetype = "dashed", size=1.2) +
  xlab("Years") +
  ylab("Rate") +
  ylim(0,6) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Sierra_obj3  <- Sierra_obj3  +
  ggtitle("Congenital - Highlands") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

# Education Selva
```{r}
education = 
  data_enaho %>%
  left_join(data_maternal_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  left_join(data_congenital_prov, by = c("year","NOMBDEP","NOMBPROV")) %>%
  select(education_level,year, region_natural, NOMBDEP,NOMBPROV,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(education_level))%>%
  filter(year > "2014") %>%
  filter(region_natural== "SELVA") %>%
  mutate(
    NOMBPROV = as.factor(NOMBPROV),
    year = as.factor(year),
    education = as.factor(education_level)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## TERCILES

Education objective 2 (terciles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_mr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <68.02 ~ "First tercile",
                             education >=68.02 & education <78.44 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

summary(education_mr$rate_mat_mean)

education_mr %>% 
     DT::datatable()
```

```{r}
Selva_obj2 =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  xlab("Years") +
  ylab("Rate") +
  ylim(0,14) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Selva_obj2  <- Selva_obj2  +
  ggtitle("Maternal - Jungle") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

Education objective 3 (terciles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_cr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_cr = education_cr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <66.20 ~ "First tercile",
                             education >=66.20 & education <76.07 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
      objective = 0.5,
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

summary(education_cr$rate_con_mean)

education_cr %>% 
     DT::datatable()
```

```{r}
Selva_obj3 =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_line(aes(y=objective),color = "black", linetype = "dashed", size=1.2) +
  xlab("Years") +
  ylab("Rate") +
  ylim(0,6) +
  theme_bw() +
  theme(
    axis.title =  element_blank(),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

Selva_obj3  <- Selva_obj3  +
  ggtitle("Congenital - Jungle") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) +
  scale_color_manual(values = selected_colors)
```

## Gráfico general
```{r, fig.height=6, fig.width=12}
combined_plot <- National_obj3 + Costa_obj3 + Sierra_obj3 + Selva_obj3 + National_obj2 + Costa_obj2 + Sierra_obj2 +  Selva_obj2 +
  plot_layout(ncol = 4, guides = 'collect') &  
  theme(legend.position = 'bottom')

Education_graph  <- combined_plot + 
  plot_annotation(
    title = "Lower education", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold")
    )
  )

Education_graph
ggsave("Lower_education.png", plot = Education_graph)
```