---
title: "Determinantes_reg_natural"
output: html_document
date: "2024-07-19"
---

```{r}
library(sf)
library(purrr)
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(readr)
library(survey)
library(gridExtra)
library(cowplot)
library(readxl)
```

```{r}
knitr::opts_chunk$set(
	echo = FALSE,
	cache = FALSE,
	dev = "png",
	dpi = 300
)
```

```{r}
data_enaho <- read_csv("Data_enaho/enaho2.csv")

data_ubigeo <- read_csv("Data_final/data_ubigeo_innovalab.csv")

departamentos <- read_sf("Límites - mapas/DEPARTAMENTOS_inei_geogpsperu_suyopomalia.shp")
#data_syphilis <- read_csv("Data_final/data_syphilis.csv")

data_enaho = rename(data_enaho, c("UBIGEO"="ubigeo"))

data_ubigeo = data_ubigeo %>%
  filter(year > 2014)

data_ubigeo = data_ubigeo [,c(8,10,12,14)]

data_ubigeo = distinct(data_ubigeo)

data_enaho <- data_enaho %>%
  left_join(data_ubigeo, by = c("UBIGEO")) %>%
  mutate(
    year = as.numeric(data_enaho$year),
    region_natural = case_when(NOMBDEP == "TUMBES"|NOMBDEP == "PIURA"|NOMBDEP == "LAMBAYEQUE"|NOMBDEP == "LA LIBERTAD"|NOMBDEP == "ANCASH"|NOMBDEP == "LIMA"|NOMBDEP == "CALLAO"|NOMBDEP == "ICA"|NOMBDEP == "AREQUIPA"|NOMBDEP == "MOQUEGUA"|NOMBDEP == "TACNA" ~ "COSTA",
                               NOMBDEP == "CAJAMARCA"|NOMBDEP == "HUANUCO"|NOMBDEP == "PASCO"|NOMBDEP == "JUNIN"|NOMBDEP == "HUANCAVELICA"|NOMBDEP == "AYACUCHO"|NOMBDEP == "APURIMAC"|NOMBDEP == "CUSCO"|NOMBDEP == "PUNO" ~ "SIERRA",
                               NOMBDEP == "AMAZONAS"|NOMBDEP == "SAN MARTIN"|NOMBDEP == "LORETO"|NOMBDEP == "UCAYALI"|NOMBDEP == "MADRE DE DIOS" ~ "SELVA")
  )

rm(data_syphilis,data_ubigeo)
```

Uploading MINSA data (maternal and congenital syphilis):
```{r, echo=FALSE}
maternal <- read_csv("Data_final/syphilis_maternal.csv")
newborn <- read_csv("Data_final/Nacidos_vivos_long.csv")
newborn_distrito <- read_excel("Data_final/Reniec_Nacimientos_Distritos.xlsx")

newborn_distrito = newborn_distrito %>% 
  mutate(across(c(NOMBDEP, NOMBPROV, NOMBDIST),
                ~ toupper(.x) %>%
                  stringi::stri_trans_general("Latin-ASCII")))

maternal = rename(
  maternal, c("NOMBDEP"="departamento","NOMBPROV"="provincia","NOMBDIST"="distrito"))
newborn = rename(
  newborn, c("NOMBDEP"="departamento","NOMBPROV"="provincia","year"="years"))

maternal_long <- pivot_longer(maternal, cols = c(4:11), 
                                names_to = "year", values_to = "maternal")

congenital <- read_csv("Data_final/syphilis_congenital.csv")

congenital <- congenital %>%
  select(!c(1))

congenital <- rename(
  congenital, c("NOMBDEP"="DEPARTAMENTO","NOMBPROV"="PROVINCIA","NOMBDIST"="DISTRITO"))

congenital_long <- pivot_longer(congenital, cols = c(4:12), 
                                names_to = "year", values_to = "congenital")

#Provincial
#newborn_prov <- newborn %>%
  #group_by(NOMBDEP, NOMBPROV, year) %>%
  #summarise(newborntotal =sum(n, na.rm = TRUE)) %>%
  #ungroup()

#Regional
newborn_dep <- newborn %>%
  group_by(NOMBDEP, year) %>%
  summarise(newborntotal =sum(n, na.rm = TRUE)) %>%
  ungroup()

#National
#newborn_nac <- newborn %>%
  #group_by(year) %>%
  #summarise(newborntotal =sum(n, na.rm = TRUE)) %>%
  #ungroup()

rm(maternal,congenital,newborn)
```

Maternal
```{r}
#data_maternal_dist <- maternal_long %>%
  #group_by(NOMBDEP, NOMBPROV, NOMBDIST, year) %>%
  #filter( year > 2014) %>%
  #summarise(maternal =sum(maternal, na.rm = TRUE)) %>%
  #mutate(year=as.numeric(year))%>%
  #ungroup()

#data_maternal_prov <- maternal_long %>%
  #group_by(NOMBDEP, NOMBPROV, year) %>%
  #filter( year > 2014) %>%
  #summarise(maternal =sum(maternal, na.rm = TRUE)) %>%
  #mutate(year=as.numeric(year))%>%
  #ungroup()

data_maternal_dep <- maternal_long %>%
  group_by(NOMBDEP, year) %>%
  filter( year > 2014) %>%
  summarise(maternal =sum(maternal, na.rm = TRUE)) %>%
  mutate(year=as.numeric(year))%>%
  ungroup()

#data_maternal_nac<- maternal_long %>%
  #group_by(year) %>%
  #filter( year > 2014) %>%
  #summarise(maternal =sum(maternal, na.rm = TRUE)) %>%
  #mutate(year=as.numeric(year))%>%
  #ungroup()

#Calculating rates of maternal syphilis 
#data_maternal_dist <- data_maternal_dist %>%
  #left_join(newborn_distrito, by = c("NOMBDEP","NOMBPROV","NOMBDIST","year")) %>%
  #filter(maternal<newborntotal&maternal!=newborntotal)%>% 
  #mutate(rate_mat = (maternal/newborntotal)*1000) 

#data_maternal_prov <- data_maternal_prov %>%
  #left_join(newborn_prov, by = c("NOMBDEP","NOMBPROV","year")) %>%
  #mutate(rate_mat = (maternal/newborntotal)*1000)

data_maternal_dep <- data_maternal_dep %>%
  left_join(newborn_dep, by = c("NOMBDEP","year")) %>%
  mutate(rate_mat = (maternal/newborntotal)*1000) %>% 
  mutate_if(is.numeric, round, 2)

#data_maternal_nac <- data_maternal_nac %>%
  #left_join(newborn_nac, by = c("year")) %>%
  #mutate(rate_mat = (maternal/newborntotal)*1000) %>% 
  #mutate_if(is.numeric, round, 2)
```

Congenital:
```{r}
congenital_long$year = as.numeric(congenital_long$year) 

#Distrital
#congenital_long_dist <- congenital_long %>%
  #group_by(NOMBDEP,NOMBPROV,NOMBDIST, year) %>%
  #filter (year >2014) %>%
  #summarise(congenital = sum(congenital, na.rm = TRUE)) %>%
  #unnest(congenital)

#data_congenital_dist <- congenital_long_dist %>%
  #left_join(newborn_distrito, by = c("NOMBDEP","NOMBPROV","NOMBDIST","year")) %>%
  #filter(congenital<newborntotal&congenital!=newborntotal)%>% 
  #mutate(rate_con = (congenital/newborntotal)*1000) %>% 
  #mutate_if(is.numeric, round, 2) 

#Provincial
#congenital_long_prov <- congenital_long %>%
  #group_by(NOMBDEP,NOMBPROV, year) %>%
  #summarise(congenital = sum(congenital, na.rm = TRUE)) %>%
  #unnest(congenital)

#data_congenital_prov <- congenital_long_prov %>%
  #left_join(newborn_prov, by = c("NOMBDEP","NOMBPROV","year")) %>%
  #mutate(rate_con = (congenital/newborntotal)*1000) %>% 
  #mutate_if(is.numeric, round, 2) %>%
  #filter(rate_con < 100.0)

#Regional
congenital_long_dep <- congenital_long %>%
  group_by(NOMBDEP,year) %>%
  summarise(congenital = sum(congenital, na.rm = TRUE)) %>%
  unnest(congenital)

data_congenital_dep <- congenital_long_dep %>%
  left_join(newborn_dep, by = c("NOMBDEP","year")) %>%
  mutate(rate_con = (congenital/newborntotal)*1000) %>% 
  mutate_if(is.numeric, round, 2) %>%
  filter(rate_con < 100.0)

#National
#congenital_long_nac <- congenital_long %>%
  #group_by(year) %>%
  #summarise(congenital = sum(congenital, na.rm = TRUE)) %>%
  #unnest(congenital)

#data_congenital_nac <- congenital_long_nac %>%
  #left_join(newborn_nac, by = c("year")) %>%
  #mutate(rate_con = (congenital/newborntotal)*1000) %>% 
  #mutate_if(is.numeric, round, 2)

rm(congenital_long,congenital_long_dep,congenital_long_nac,newborn_nac,newborn_dep,data_ins_long,newborn_nac,newborn_dep)
```

# Poverty National
```{r}
library(RSQLite)
poverty = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(poverty,year, region_natural, NOMBDEP,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(poverty))%>%
  filter(year > "2014") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    poverty = as.factor(poverty)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## QUANTILES

Poverty objective 2 (quantiles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(poverty_mr$povertypoor)*100,2)

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <12.09~ "First quartile",
                            poverty >=12.09 & poverty <19.89 ~ "Second quantile",
                            poverty >=19.89 & poverty <=28.24 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
    )

poverty_mr %>% 
     DT::datatable()
```

```{r}
poverty_mrg =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_mrg <- poverty_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty objective 3 (quantiles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(poverty_cr$povertypoor)*100,2)

poverty_cr = poverty_cr %>%  
mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <12.09 ~ "First quartile",
                            poverty >=12.09 & poverty <19.89 ~ "Second quantile",
                            poverty >=19.89 & poverty <=27.76 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

poverty_cr %>% 
     DT::datatable()
```

```{r}
poverty_crg =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_crg <- poverty_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
library(patchwork)
combined_plot <- poverty_mrg + poverty_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

National4  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Poverty at the National Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
National4
```

## TERCILES

Poverty objective 2 (terciles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_mr$povertypoor, probs = c(1/3, 2/3))*100

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <15.06 ~ "First tercile",
                            poverty >=15.06 & poverty <25.09 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

poverty_mr %>% 
     DT::datatable()
```

```{r}
poverty_mrg =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_mrg <- poverty_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty objective 3 (terciles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_cr$povertypoor, probs = c(1/3, 2/3))*100

poverty_cr = poverty_cr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <15.57 ~ "First tercile",
                            poverty >=15.57 & poverty <24.98 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
  summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

poverty_cr %>% 
     DT::datatable()
```

```{r}
poverty_crg =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_crg <- poverty_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
library(patchwork)
combined_plot <- poverty_mrg + poverty_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

National3  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Poverty at the National Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
National3
```

# Poverty Costa
```{r}
poverty = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(poverty,year, region_natural, NOMBDEP,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(poverty))%>%
  filter(year > "2014") %>%
  filter(region_natural== "COSTA") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    poverty = as.factor(poverty)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## QUANTILES

Poverty Costa objective 2 (quantiles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(poverty_mr$povertypoor)*100,2)

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <9.26 ~ "First quartile",
                            poverty >=9.26 & poverty <12.83 ~ "Second quantile",
                            poverty >=12.83 & poverty <=19.61 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
  )

poverty_mr %>% 
     DT::datatable()
```

```{r}
poverty_mrg =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_mrg <- poverty_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty Costa objective 3 (quantiles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(poverty_cr$povertypoor)*100,2)

poverty_cr = poverty_cr %>%  
mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <9.04 ~ "First quartile",
                            poverty >=9.04 & poverty <12.69 ~ "Second quantile",
                            poverty >=12.69 & poverty <=19.53 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

poverty_cr %>% 
     DT::datatable()
```

```{r}
poverty_crg =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_crg <- poverty_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- poverty_mrg + poverty_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Costa4  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Poverty at Costa Region", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Costa4
```

## TERCILES

Poverty Costa objective 2 (terciles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_mr$povertypoor, probs = c(1/3, 2/3))*100

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <10.07 ~ "First tercile",
                            poverty >=10.07 & poverty <17.52 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

poverty_mr %>% 
     DT::datatable()
```

```{r}
poverty_mrg =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_mrg <- poverty_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty Costa objective 3 (terciles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_cr$povertypoor, probs = c(1/3, 2/3))*100

poverty_cr = poverty_cr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <9.93 ~ "First tercile",
                            poverty >=9.93 & poverty <17.05 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
  summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

poverty_cr %>% 
     DT::datatable()
```

```{r}
poverty_crg =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_crg <- poverty_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- poverty_mrg + poverty_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Costa3  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Poverty at Costa Region", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Costa3
```

# Poverty Sierra
```{r}
poverty = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(poverty,year, region_natural, NOMBDEP,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(poverty))%>%
  filter(year > "2014") %>%
  filter(region_natural== "SIERRA") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    poverty = as.factor(poverty)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## QUANTILES

Poverty Sierra objective 2 (quantiles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(poverty_mr$povertypoor)*100,2)

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <25.03 ~ "First quartile",
                            poverty >=25.03 & poverty <30.80 ~ "Second quantile",
                            poverty >=30.80 & poverty <=35.75 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
  )

poverty_mr %>% 
     DT::datatable()
```

```{r}
poverty_mrg =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_mrg <- poverty_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty Sierra objective 3 (quantiles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(poverty_cr$povertypoor)*100,2)

poverty_cr = poverty_cr %>%  
mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <24.94 ~ "First quartile",
                            poverty >=24.94 & poverty <30.68 ~ "Second quantile",
                            poverty >=30.68 & poverty <=35.66 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

poverty_cr %>% 
     DT::datatable()
```

```{r}
poverty_crg =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_crg <- poverty_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- poverty_mrg + poverty_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Sierra4  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Poverty at Sierra Region", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Sierra4
```

## TERCILES

Poverty Sierra objective 2 (terciles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_mr$povertypoor, probs = c(1/3, 2/3))*100

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <28.18 ~ "First tercile",
                            poverty >=28.18 & poverty <34.96 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

poverty_mr %>% 
     DT::datatable()
```

```{r}
poverty_mrg =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_mrg <- poverty_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty Sierra objective 3 (terciles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_cr$povertypoor, probs = c(1/3, 2/3))*100

poverty_cr = poverty_cr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <28.15 ~ "First tercile",
                            poverty >=28.15 & poverty <33.85 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
  summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

poverty_cr %>% 
     DT::datatable()
```

```{r}
poverty_crg =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_crg <- poverty_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- poverty_mrg + poverty_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Sierra3  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Poverty at Sierra Region", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Sierra3
```

# Poverty Selva
```{r}
poverty = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(poverty,year, region_natural, NOMBDEP,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(poverty))%>%
  filter(year > "2014") %>%
  filter(region_natural== "SELVA") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    poverty = as.factor(poverty)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## QUANTILES

Poverty Selva objective 2 (quantiles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(poverty_mr$povertypoor)*100,2)

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <11.33 ~ "First quartile",
                            poverty >=11.33 & poverty <20.54 ~ "Second quantile",
                            poverty >=20.54 & poverty <=25.32 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
  )

poverty_mr %>% 
     DT::datatable()
```

```{r}
poverty_mrg =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_mrg <- poverty_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty Selva objective 3 (quantiles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(poverty_cr$povertypoor)*100,2)

poverty_cr = poverty_cr %>%  
mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <10.21 ~ "First quartile",
                            poverty >=10.21 & poverty <19.72 ~ "Second quantile",
                            poverty >=19.72 & poverty <=24.79 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

poverty_cr %>% 
     DT::datatable()
```

```{r}
poverty_crg =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_crg <- poverty_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- poverty_mrg + poverty_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Selva4  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Poverty at Selva Region", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Selva4
```

## TERCILES

Poverty Selva objective 2 (terciles)
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_mr$povertypoor, probs = c(1/3, 2/3))*100

poverty_mr = poverty_mr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <14.75 ~ "First tercile",
                            poverty >=14.75 & poverty <23.02 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

poverty_mr %>% 
     DT::datatable()
```

```{r}
poverty_mrg =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_mrg <- poverty_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty Selva objective 3 (terciles)
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~poverty, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(poverty_cr$povertypoor, probs = c(1/3, 2/3))*100

poverty_cr = poverty_cr %>%  
  mutate(
    poverty = povertypoor*100,
    poverty_cod = case_when(poverty <12.26 ~ "First tercile",
                            poverty >=12.26 & poverty <23.02 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(poverty_cod))%>%
  group_by(year,poverty_cod)%>%
  summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

poverty_cr %>% 
     DT::datatable()
```

```{r}
poverty_crg =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = poverty_cod))+
  geom_line(size = 1.2, aes(col = poverty_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

poverty_crg <- poverty_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- poverty_mrg + poverty_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Selva3  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Poverty at Selva Region", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Selva3
```

# Education National
```{r}
education = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(education_level,year, region_natural, NOMBDEP,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(education_level))%>%
  filter(year > "2014") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    education = as.factor(education_level)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## QUANTILES

Education objective 2 (quantiles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(education_mr$`educationless than secondary`)*100,2)

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <52.37 ~ "First quartile",
                            education >=52.37 & education <62.29 ~ "Second quantile",
                            education >=62.29 & education <=70.96 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
  )

education_mr %>% 
     DT::datatable()
```

```{r}
education_mrg =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_mrg <- education_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Education objective 3 (quantiles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(education_cr$`educationless than secondary`)*100,2)

education_cr = education_cr %>%  
mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <54.47 ~ "First quartile",
                            education >=54.47 & education <62.29 ~ "Second quantile",
                            education >=62.29 & education <=70.24 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

education_cr %>% 
     DT::datatable()
```

```{r}
education_crg =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_crg <- education_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- education_mrg + education_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

National4b <- combined_plot + 
  plot_annotation(
    title = "Objectives by Education at the National Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
National4b
```

## TERCILES

Poverty objective 2 (terciles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_mr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <57.21 ~ "First tercile",
                             education >=57.21 & education <67.89 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

education_mr %>% 
     DT::datatable()
```

```{r}
education_mrg =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

educationy_mrg <- education_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty objective 3 (terciles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_cr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_cr = education_cr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <57.48 ~ "First tercile",
                             education >=57.48 & education <67.17 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

education_cr %>% 
     DT::datatable()
```

```{r}
education_crg =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_crg <- education_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- education_mrg + education_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

National3b <- combined_plot + 
  plot_annotation(
    title = "Objectives by Education at the National Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
National3b
```

# Education Costa
```{r}
education = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(education_level,year, region_natural, NOMBDEP,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(education_level))%>%
  filter(year > "2014") %>%
  filter(region_natural== "COSTA") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    education = as.factor(education_level)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## QUANTILES

Costa Education objective 2 (quantiles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(education_mr$`educationless than secondary`)*100,2)

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <40.05 ~ "First quartile",
                            education >=40.05 & education <50.71 ~ "Second quantile",
                            education >=50.71 & education <=58.24 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
  )

education_mr %>% 
     DT::datatable()
```

```{r}
education_mrg =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_mrg <- education_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Costa Education objective 3 (quantiles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(education_cr$`educationless than secondary`)*100,2)

education_cr = education_cr %>%  
mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <39.32 ~ "First quartile",
                            education >=39.32 & education <51.28 ~ "Second quantile",
                            education >=51.28 & education <=58.79 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

education_cr %>% 
     DT::datatable()
```

```{r}
education_crg =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_crg <- education_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- education_mrg + education_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Costa4b  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Education at Costa Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Costa4b
```

## TERCILES

Costa Poverty objective 2 (terciles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_mr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <42.67 ~ "First tercile",
                             education >=42.67 & education <55.78 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

education_mr %>% 
     DT::datatable()
```

```{r}
education_mrg =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

educationy_mrg <- education_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Costa Poverty objective 3 (terciles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_cr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_cr = education_cr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <43.33 ~ "First tercile",
                             education >=43.33 & education <56.76 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

education_cr %>% 
     DT::datatable()
```

```{r}
education_crg =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_crg <- education_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- education_mrg + education_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Costa3b  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Education at Costa Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Costa3b
```

# Education Sierra
```{r}
education = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(education_level,year, region_natural, NOMBDEP,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(education_level))%>%
  filter(year > "2014") %>%
  filter(region_natural== "SIERRA") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    education = as.factor(education_level)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## QUANTILES

Sierra Education objective 2 (quantiles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(education_mr$`educationless than secondary`)*100,2)

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <63.98 ~ "First quartile",
                            education >=63.98 & education <72.40 ~ "Second quantile",
                            education >=72.40 & education <=76.50 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
  )

education_mr %>% 
     DT::datatable()
```

```{r}
education_mrg =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_mrg <- education_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Sierra Education objective 3 (quantiles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(education_cr$`educationless than secondary`)*100,2)

education_cr = education_cr %>%  
mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <63.98 ~ "First quartile",
                            education >=63.98 & education <71.79 ~ "Second quantile",
                            education >=71.79 & education <=75.98 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

education_cr %>% 
     DT::datatable()
```

```{r}
education_crg =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_crg <- education_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- education_mrg + education_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Sierra4b  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Education at Sierra Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Sierra4b
```

## TERCILES

Sierra Poverty objective 2 (terciles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_mr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <68.16 ~ "First tercile",
                             education >=68.16 & education <75.13 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

education_mr %>% 
     DT::datatable()
```

```{r}
education_mrg =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

educationy_mrg <- education_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Sierra Poverty objective 3 (terciles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_cr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_cr = education_cr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <67.74 ~ "First tercile",
                             education >=67.74 & education <74.50 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

education_cr %>% 
     DT::datatable()
```

```{r}
education_crg =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_crg <- education_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- education_mrg + education_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Sierra3b  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Education at Sierra Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Sierra3b
```

# Education Selva
```{r}
education = 
  data_enaho %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(education_level,year, region_natural, NOMBDEP,conglome,estrato,facpob07,rate_mat,rate_con) %>%
  filter(!is.na(education_level))%>%
  filter(year > "2014") %>%
  filter(region_natural== "SELVA") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    education = as.factor(education_level)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ conglome, strata = ~ estrato, weights = ~ facpob07, data = .x))
  )

options(survey.lonely.psu="remove")
```

## QUANTILES

Selva Education objective 2 (quantiles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(education_mr$`educationless than secondary`)*100,2)

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <63.07 ~ "First quartile",
                            education >=63.07 & education <67.74 ~ "Second quantile",
                            education >=67.74 & education <=71.67 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
  )

education_mr %>% 
     DT::datatable()
```

```{r}
education_mrg =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_mrg <- education_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Selva Education objective 3 (quantiles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

round(summary(education_cr$`educationless than secondary`)*100,2)

education_cr = education_cr %>%  
mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <62.62 ~ "First quartile",
                            education >=62.62 & education <67.62 ~ "Second quantile",
                            education >=67.62 & education <=71.67 ~ "Third quantile",
                            TRUE ~ "Fourth quantile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

education_cr %>% 
     DT::datatable()
```

```{r}
education_crg =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_crg <- education_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- education_mrg + education_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Selva4b  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Education at Selva Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Selva4b
```

## TERCILES

Poverty objective 2 (terciles)
```{r}
education_mr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_mat , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_mr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_mr = education_mr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <64.78 ~ "First tercile",
                             education >=64.78 & education <70.32 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_mat_mean = mean(rate_mat),
    ci_lower = ifelse(mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())<0,0,mean(rate_mat) - qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())),
    ci_upper = mean(rate_mat) + qt(0.975, df = n() - 1) * sd(rate_mat) / sqrt(n())
            )

education_mr %>% 
     DT::datatable()
```

```{r}
education_mrg =
  ggplot(data = education_mr,aes(x = year, y = rate_mat_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

educationy_mrg <- education_mrg +
  ggtitle("Objective Two") +
  theme(
    plot.title = element_text(size = 10), 
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1))
```

Poverty objective 3 (terciles)
```{r}
education_cr = 
  education %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~education, by =~rate_con , design = .x, FUN =svymean, deff=TRUE) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

quantile(education_cr$`educationless than secondary`, probs = c(1/3, 2/3))*100

education_cr = education_cr %>%  
  mutate(
    education = `educationless than secondary`*100,
    education_cod = case_when(education <63.29 ~ "First tercile",
                             education >=63.29 & education <70.32 ~ "Second tercile",
                            TRUE ~ "Third tercile")) %>%
  filter(!is.na(education_cod))%>%
  group_by(year,education_cod)%>%
    summarize(
    rate_con_mean = mean(rate_con),
    ci_lower = ifelse(mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())<0,0,mean(rate_con) - qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())),
    ci_upper = mean(rate_con) + qt(0.975, df = n() - 1) * sd(rate_con) / sqrt(n())
            )

education_cr %>% 
     DT::datatable()
```

```{r}
education_crg =
  ggplot(data = education_cr,aes(x = year, y = rate_con_mean, group = education_cod))+
  geom_line(size = 1.2, aes(col = education_cod))+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
  xlab("Years") +
  ylab("Rate") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

education_crg <- education_crg +
  ggtitle("Objective Three") +
  theme(
    plot.title = element_text(size = 10),  
    legend.position = "bottom", 
    legend.justification = "center") +
  guides(fill = guide_legend(nrow = 1)) 
```

```{r}
combined_plot <- education_mrg + education_crg + 
  plot_layout(guides = 'collect') & 
  theme(legend.position = 'bottom')

Selva3b  <- combined_plot + 
  plot_annotation(
    title = "Objectives by Education at Selva Level", 
    theme = theme(
      plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
      plot.margin = margin(5, 5, 5, 5)  
    )
  )
Selva3b
```

#Cuartiles total
```{r}
National4
National4b
Costa4
Costa4b
Sierra4
Sierra4b
Selva4
Selva4b
```

#Terciles total
```{r}
National3
National3b
Costa3
Costa3b
Sierra3
Sierra3b
Selva3
Selva3b
```
