---
title: "Tendencias_determinantes"
output: html_document
date: "2024-02-14"
---

```{r}
library(sf)
library(purrr)
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(readr)
library(survey)
library(gridExtra)
library(cowplot)
```

```{r}
knitr::opts_chunk$set(
	echo = FALSE,
	cache = FALSE,
	dev = "png",
	dpi = 300
)
```

Uploading ENDES data:
 
```{r, echo =FALSE}
data_ubigeo <- read_csv("Data_final/data_ubigeo_innovalab.csv")
data_ubigeo_2022_innova <- read_csv("Data_final/data_ubigeo_2022_innova.csv")

data_ubigeo_2022_innova = data_ubigeo_2022_innova[,c(2:6,1,7:9)]
data_ubigeo = data_ubigeo[,c(1:6,8,10,12)]

data_ubigeo_2022_innova = rename(data_ubigeo_2022_innova, c("NOMBDEP"="DEPARTAMEN","NOMBPROV"="PROVINCIA","NOMBDIST"="DISTRITO"))

data_ubigeo = rbind(data_ubigeo,data_ubigeo_2022_innova)

rm(data_ubigeo_2022_innova)

departamentos <- read_sf("Límites - mapas/DEPARTAMENTOS_inei_geogpsperu_suyopomalia.shp")
data_syphilis <- read_csv("Data_final/data_syphilis.csv")

data_endes <- data_syphilis%>% 
  left_join(data_ubigeo, by = c("caseid","year"))

data_endes <- data_endes %>%
  left_join(departamentos, by = c("NOMBDEP"))

rm(data_syphilis,data_ubigeo,departamentos)
```

Uploading MINSA data (maternal and congenital syphilis):

```{r, echo=FALSE}
data_ins_long <- read_csv("Data_final/ins_final_long.csv")
newborn <- read_csv("Data_final/Nacidos_vivos_long.csv")

data_ins_long = rename(
  data_ins_long, c("NOMBDEP"="departamento","NOMBPROV"="provincia","NOMBDIST"="distrito"))
newborn = rename(
  newborn, c("NOMBDEP"="departamento","NOMBPROV"="provincia","year"="years"))

congenital <- read_csv("Data_final/syphilis_congenital.csv")

congenital <- congenital %>%
  select(!c(1))

congenital <- rename(
  congenital, c("NOMBDEP"="DEPARTAMENTO","NOMBPROV"="PROVINCIA","NOMBDIST"="DISTRITO"))

congenital_long <- pivot_longer(congenital, cols = c(4:12), 
                                names_to = "year", values_to = "congenital")

#Regional
newborn_dep <- newborn %>%
  group_by(NOMBDEP, year) %>%
  summarise(newborntotal =sum(n, na.rm = TRUE)) %>%
  ungroup()

#National
newborn_nac <- newborn %>%
  group_by(year) %>%
  summarise(newborntotal =sum(n, na.rm = TRUE)) %>%
  ungroup()

rm(congenital,newborn)
```

Maternal 

```{r}
data_maternal_dep <- data_ins_long %>%
  group_by(NOMBDEP, year) %>%
  filter( year > 2013) %>%
  summarise(tamizaje_reactivo =sum(tamizaje_reactivo)) %>%
  ungroup()

data_maternal_nac<- data_ins_long %>%
  group_by(year) %>%
  filter( year > 2013) %>%
  summarise(tamizaje_reactivo =sum(tamizaje_reactivo)) %>%
  ungroup()

#Calculating rates of maternal syphilis 
data_maternal_dep <- data_maternal_dep %>%
  left_join(newborn_dep, by = c("NOMBDEP","year")) %>%
  mutate(rate_mat = (tamizaje_reactivo/newborntotal)*1000)

data_maternal_nac <- data_maternal_nac %>%
  left_join(newborn_nac, by = c("year")) %>%
  mutate(rate_mat = (tamizaje_reactivo/newborntotal)*1000)
```

Congenital:

```{r}
congenital_long$year = as.numeric(congenital_long$year) 

#Regional
congenital_long_dep <- congenital_long %>%
  group_by(NOMBDEP,year) %>%
  summarise(congenital = sum(congenital, na.rm = TRUE)) %>%
  unnest(congenital)

data_congenital_dep <- congenital_long_dep %>%
  left_join(newborn_dep, by = c("NOMBDEP","year")) %>%
  mutate(rate_con = (congenital/newborntotal)*1000) %>% 
  mutate_if(is.numeric, round, 2) %>%
  filter(rate_con < 100.0)

#National
congenital_long_nac <- congenital_long %>%
  mutate(
  congenital = ifelse(year==2014&NOMBPROV=="BARRANCA",NA,congenital_long$congenital))%>%
  group_by(year) %>%
  summarise(congenital = sum(congenital, na.rm = TRUE)) %>%
  unnest(congenital)

data_congenital_nac <- congenital_long_nac %>%
  left_join(newborn_nac, by = c("year")) %>%
  mutate(rate_con = (congenital/newborntotal)*1000) %>% 
  mutate_if(is.numeric, round, 2)

rm(congenital_long,congenital_long_dep,congenital_long_nac,newborn_nac,newborn_dep,data_ins_long,newborn_nac,newborn_dep)
```

```{r}
data_endes <- data_endes %>%
  mutate(
    syphilis_screening=ifelse(syphilis_screening=="Yes",1, 0)
  )

data_endes$syphilis_screening <- ifelse(is.na(data_endes$syphilis_screening),0,data_endes$syphilis_screening)

data_endes$syphilis_screening = as.factor(data_endes$syphilis_screening)
```

## wealth_index 

```{r}
library(RSQLite)
poverty = 
  data_endes %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(wealth_index,year,NOMBDEP,v001,v022,v005,syphilis_screening,rate_mat,rate_con) %>%
  filter(!is.na(wealth_index))%>%
  filter(year > "2013") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    wealth_index = as.factor(wealth_index)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ v001, strata = ~ v022, weights = ~ v005, data = .x))
  )

options(survey.lonely.psu="remove")
```

Wealth index objective 1
```{r}
poverty_sc = 
  poverty %>%
  group_by(year) %>%
  mutate(
    syphilis = map(.x = df,
              .f = ~svyby(~as.factor(syphilis_screening), by = ~wealth_index, design = .x, FUN =svyciprop, vartype=c('se','ci')) %>% 
                as.data.frame())
  ) %>%
  unnest(syphilis) 
options(survey.lonely.psu="remove")

poverty_sc %>% 
  mutate(
    across(`as.factor(syphilis_screening)`:ci_u,.fns = ~round(.,3)*100)) %>% 
  
    DT::datatable()
```

```{r}
poverty_scg =
  ggplot(data = poverty_sc,aes(x = year, y = `as.factor(syphilis_screening)`, ymin = ci_l, ymax = ci_u, group = wealth_index))+
  geom_line(size = 1.2, aes(col = wealth_index))+
  geom_ribbon(aes(fill = wealth_index), alpha = 0.1)+
  xlab("Years") +
  ylab("Prop. %") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

#ggsave("wealth_obj1.png", plot = poverty_scg, width = 8, height = 4, dpi = 300)
```

Wealth index objective 2
```{r}
poverty_mr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~wealth_index, by =~rate_mat , design = .x, FUN =svymean) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

poverty_mr = poverty_mr %>%  
  mutate(
    wealth_index = ifelse(wealth_indexRichest > wealth_indexRich & wealth_indexRichest > wealth_indexMiddle & wealth_indexRichest > wealth_indexPoor & wealth_indexRichest > wealth_indexPoorest, "Richest", ifelse(wealth_indexRich > wealth_indexRichest & wealth_indexRich > wealth_indexMiddle & wealth_indexRich > wealth_indexPoor & wealth_indexRich > wealth_indexPoorest, "Rich", ifelse(wealth_indexMiddle > wealth_indexRichest & wealth_indexMiddle > wealth_indexRich & wealth_indexMiddle > wealth_indexPoor & wealth_indexMiddle > wealth_indexPoorest,"Middle",ifelse(wealth_indexPoor > wealth_indexRichest & wealth_indexPoor > wealth_indexRich & wealth_indexPoor > wealth_indexMiddle & wealth_indexPoor > wealth_indexPoorest,"Poor", ifelse(wealth_indexPoorest > wealth_indexRichest & wealth_indexPoorest > wealth_indexRich & wealth_indexPoorest > wealth_indexMiddle & wealth_indexPoorest > wealth_indexPoor,"Poorest", NA )))))) %>%
  group_by(year,wealth_index)%>%
  summarize(rate_mat_mean=mean(rate_mat))

poverty_mr %>% 
     DT::datatable()
``` 


```{r}
poverty_mrg =
  ggplot(data = poverty_mr,aes(x = year, y = rate_mat_mean, group = wealth_index))+
  geom_line(size = 1.2, aes(col = wealth_index))+
  xlab("Years") +
  ylab("Prop. %") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

#ggsave("dep_wealth_obj2.png", plot = poverty_mrg, width = 8, height = 4, dpi = 300)
```

Wealth index objective 3
```{r}
poverty_cr = 
  poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~wealth_index, by =~rate_con , design = .x, FUN =svymean) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

poverty_cr = poverty_cr %>%  
  mutate(
    wealth_index = ifelse(wealth_indexRichest > wealth_indexRich & wealth_indexRichest > wealth_indexMiddle & wealth_indexRichest > wealth_indexPoor & wealth_indexRichest > wealth_indexPoorest, "Richest", ifelse(wealth_indexRich > wealth_indexRichest & wealth_indexRich > wealth_indexMiddle & wealth_indexRich > wealth_indexPoor & wealth_indexRich > wealth_indexPoorest, "Rich", ifelse(wealth_indexMiddle > wealth_indexRichest & wealth_indexMiddle > wealth_indexRich & wealth_indexMiddle > wealth_indexPoor & wealth_indexMiddle > wealth_indexPoorest,"Middle",ifelse(wealth_indexPoor > wealth_indexRichest & wealth_indexPoor > wealth_indexRich & wealth_indexPoor > wealth_indexMiddle & wealth_indexPoor > wealth_indexPoorest,"Poor", ifelse(wealth_indexPoorest > wealth_indexRichest & wealth_indexPoorest > wealth_indexRich & wealth_indexPoorest > wealth_indexMiddle & wealth_indexPoorest > wealth_indexPoor,"Poorest", NA ))))))%>%
  group_by(year,wealth_index)%>%
  summarize(rate_con_mean=mean(rate_con))

poverty_mr %>% 
     DT::datatable()
```

```{r}
poverty_crg =
  ggplot(data = poverty_cr,aes(x = year, y = rate_con_mean, group = wealth_index))+
  geom_line(size = 1.2, aes(col = wealth_index))+
  xlab("Years") +
  ylab("Prop. %") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )

#ggsave("dep_wealth_obj3.png", plot = poverty_crg, width = 8, height = 4, dpi = 300)
```

final_nac_plot = ggdraw() +
  draw_plot(peru1, 0, .14, .3, .8) +
  draw_plot(peru2, .3, 0, .3, .95) +
  draw_plot(peru3, .6, .14, .3, .8) +
  draw_plot_label(c("Peru objective 1","Peru objective 2","Peru objective 3"),c(0,.3,.6),c(.99,.99,.99),size=10)

final_nac_plot

## Wealth index base AMAZONAS
```{r}
dep_poverty = 
  data_endes %>%
  left_join(data_maternal_dep, by = c("year","NOMBDEP")) %>%
  left_join(data_congenital_dep, by = c("year","NOMBDEP")) %>%
  select(wealth_index,year,NOMBDEP,v001,v022,v005,syphilis_screening,rate_mat,rate_con) %>%
  filter(!is.na(wealth_index))%>%
  filter(year > "2013") %>%
  filter(NOMBDEP== "AMAZONAS") %>%
  mutate(
    NOMBDEP = as.factor(NOMBDEP),
    year = as.factor(year),
    wealth_index = as.factor(wealth_index)
  ) %>%
  group_by(year) %>%
  nest() %>%
  mutate(
    df = map(.x=data,
             .f = ~svydesign(id = ~ v001, strata = ~ v022, weights = ~ v005, data = .x))
  )

options(survey.lonely.psu="remove")
```

#### Wealth index objective 1 AMAZONAS
```{r}
dep_poverty_sc = 
  dep_poverty %>%
  group_by(year) %>%
  mutate(
    syphilis = map(.x = df,
              .f = ~svyby(~as.factor(syphilis_screening), by = ~wealth_index, design = .x, FUN =svyciprop, vartype=c('se','ci')) %>% 
                as.data.frame())
  ) %>%
  unnest(syphilis) 
options(survey.lonely.psu="remove")

dep_poverty_sc %>% 
  mutate(
    across(`as.factor(syphilis_screening)`:ci_u,.fns = ~round(.,3)*100)) %>% 
  
    DT::datatable()
```

```{r}
dep_poverty_scg =
  ggplot(data = dep_poverty_sc,aes(x = year, y = `as.factor(syphilis_screening)`, ymin = ci_l, ymax = ci_u, group = wealth_index))+
  geom_line(size = 1.2, aes(col = wealth_index))+
  geom_ribbon(aes(fill = wealth_index), alpha = 0.1)+
  xlab("Years") +
  ylab("Prop. %") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )
```

#### Wealth index objective 2 AMAZONAS
```{r}
dep_poverty_mr = 
  dep_poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~wealth_index, by =~rate_mat , design = .x, FUN =svymean) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

dep_poverty_mr = dep_poverty_mr %>%  
  mutate(
    wealth_index = ifelse(wealth_indexRichest > wealth_indexRich & wealth_indexRichest > wealth_indexMiddle & wealth_indexRichest > wealth_indexPoor & wealth_indexRichest > wealth_indexPoorest, "Richest", ifelse(wealth_indexRich > wealth_indexRichest & wealth_indexRich > wealth_indexMiddle & wealth_indexRich > wealth_indexPoor & wealth_indexRich > wealth_indexPoorest, "Rich", ifelse(wealth_indexMiddle > wealth_indexRichest & wealth_indexMiddle > wealth_indexRich & wealth_indexMiddle > wealth_indexPoor & wealth_indexMiddle > wealth_indexPoorest,"Middle",ifelse(wealth_indexPoor > wealth_indexRichest & wealth_indexPoor > wealth_indexRich & wealth_indexPoor > wealth_indexMiddle & wealth_indexPoor > wealth_indexPoorest,"Poor", ifelse(wealth_indexPoorest > wealth_indexRichest & wealth_indexPoorest > wealth_indexRich & wealth_indexPoorest > wealth_indexMiddle & wealth_indexPoorest > wealth_indexPoor,"Poorest", NA )))))) %>%
  group_by(year,wealth_index)%>%
  summarize(rate_mat_mean=mean(rate_mat))

dep_poverty_mr %>% 
     DT::datatable()
``` 

```{r}
dep_poverty_mrg =
  ggplot(data = dep_poverty_mr,aes(x = year, y = rate_mat_mean, group = wealth_index))+
  geom_line(size = 1.2, aes(col = wealth_index))+
  xlab("Years") +
  ylab("Prop. %") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )
```

Wealth index objective 3 AMAZONAS
```{r}
dep_poverty_cr = 
  dep_poverty %>%
  group_by(year) %>%
  mutate(
    wi = map(.x = df,
              .f = ~svyby(~wealth_index, by =~rate_con , design = .x, FUN =svymean) %>% 
                as.data.frame())
  ) %>%
  unnest(wi) 
options(survey.lonely.psu="remove")

dep_poverty_cr = dep_poverty_cr %>%  
  mutate(
    wealth_index = ifelse(wealth_indexRichest > wealth_indexRich & wealth_indexRichest > wealth_indexMiddle & wealth_indexRichest > wealth_indexPoor & wealth_indexRichest > wealth_indexPoorest, "Richest", ifelse(wealth_indexRich > wealth_indexRichest & wealth_indexRich > wealth_indexMiddle & wealth_indexRich > wealth_indexPoor & wealth_indexRich > wealth_indexPoorest, "Rich", ifelse(wealth_indexMiddle > wealth_indexRichest & wealth_indexMiddle > wealth_indexRich & wealth_indexMiddle > wealth_indexPoor & wealth_indexMiddle > wealth_indexPoorest,"Middle",ifelse(wealth_indexPoor > wealth_indexRichest & wealth_indexPoor > wealth_indexRich & wealth_indexPoor > wealth_indexMiddle & wealth_indexPoor > wealth_indexPoorest,"Poor", ifelse(wealth_indexPoorest > wealth_indexRichest & wealth_indexPoorest > wealth_indexRich & wealth_indexPoorest > wealth_indexMiddle & wealth_indexPoorest > wealth_indexPoor,"Poorest", NA ))))))%>%
  group_by(year,wealth_index)%>%
  summarize(rate_con_mean=mean(rate_con))

dep_poverty_mr %>% 
     DT::datatable()
```


```{r}
dep_poverty_crg =
  ggplot(data = dep_poverty_cr,aes(x = year, y = rate_con_mean, group = wealth_index))+
  geom_line(size = 1.2, aes(col = wealth_index))+
  xlab("Years") +
  ylab("Prop. %") +
  theme_bw() +
  theme(
    axis.title = element_text(face ="bold", size = 11),
    legend.text = element_text(size = 8, face = "bold"),
    axis.text = element_text(face = "bold", family = "Arial"),
    axis.text.x = element_text( size = 9),
    legend.position = "top",
    legend.title = element_blank(),
    axis.line = element_line(colour = "black", size = 1),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    panel.grid = element_blank()
  )
```